Residence time, a master variable of ecology, physiology, and natural selection

### 2015-08-29 analyses/2015_06_27_ResTime.Rmd

source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")

@@

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/IndRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  cts <- c(cts, line[1])
  sims <- c(sims, line[2])
  rtd <- line[-1:-2]
  ind.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/TracerRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  tracer.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/ResRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  res.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=6, fig.height=6}

>>>>

@@

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/IndRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  cts <- c(cts, line[1])
  sims <- c(sims, line[2])
  rtd <- line[-1:-2]
  ind.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/TracerRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  tracer.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/ResRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  res.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=6, fig.height=6}
plot.new()
